Automatic conversion of colloquial Finnish to standard Finnish

### 2015-01-26 finnormal-nodalida-2015/finnormal2015.tex
fix bigram example
git-svn-id: https://svn.code.sf.net/p/apertium/svn/branches/papers/@58586 72bbbca6-d526-0410-a7d9-f06f51895060

\newcite{nakov2012} present a method of statistical machine translation on the character level between related languages that takes advantage of phrase-based machine translation architecture. The method relies on preprocessing the input and output by inserting spaces in between the characters of words, for example the string `M\"{a} meen Helsinkiin' would become `M \"{a} \$ m e e n \$ H e l s i n k i i n' with a unigram model, or `M\"{a} \$ me en \$ He ls in ki in' with a bigram model.

>>>>

\newcite{nakov2012} present a method of statistical machine translation on the character level between related languages that takes advantage of phrase-based machine translation architecture. The method relies on preprocessing the input and output by inserting spaces in between the characters of words, for example the string `m\"{a} meen Helsinkiin' would become `m \"{a} \$ m e e n \$ H e l s i n k i i n' with a unigram model, or `m\"{a} \"{a}\$ \$m me ee en n\$ \$H He el ls si in nk ki ii in' with a bigram model.
